|

### 2023-04-11 paper/04-results.Rmd
outlined stability section

Further, Figure \ref{fig:fig_outcome_curves} shows the positional STRAIN curves by whether a play's outcome is a hit, sack, hurry, or none of those.

@@

Since STRAIN is observed continuously for every play in our data, this allows us to aggregate across all frames played and compute the average STRAIN for NFL pass rushers over the course of the eight-week sample size.

(maybe some math)

Based on the clearly distinct patterns for different positions as previously observed, we evaluate interior pass-rushers (NT's and DT's) separately from edge rushers (OLB's and DE's).
Tables \ref{tab:edge} and \ref{tab:interior} are leaderboards for the NFL's best edge and interior rushers (with at least 100 plays) rated by the average STRAIN across all frames for the first eight weeks of the 2021 regular season.

@@

@@

Figure \ref{fig:fig_cor_pressure} shows cor with pressure
We observe a fairly strong correlation (r = 0.625) between average STRAIN and pressure rate.

>>>>

Further, Figure \ref{fig:fig_outcome_curves} shows the positional STRAIN curves by whether a play's outcome is a hit, sack, hurry, or none of those. 
It is striking that for plays with sack outcome,

@@

Since STRAIN is observed continuously for every play in our data, this allows us to aggregate across all frames played and compute the average STRAIN for NFL pass rushers over the course of the eight-week sample size.
Based on the clearly distinct patterns for different positions as previously observed, we evaluate interior pass-rushers (NT's and DT's) separately from edge rushers (OLB's and DE's).
Tables \ref{tab:edge} and \ref{tab:interior} are leaderboards for the NFL's best edge and interior rushers (with at least 100 plays) rated by the average STRAIN across all frames for the first eight weeks of the 2021 regular season.

@@

Next, we examine the predictability of STRAIN as a measure of pressure.
We first look at how well strain correlates with a simple measure of pressure rate, defined as the total hits, sacks and hurries per snap.
Figure \ref{fig:fig_cor_pressure} shows a scatterplot of average STRAIN and pressure rate.
We observe a fairly strong correlation (r = 0.625)...

Furthermore, first 4 weeks’ avg STRAIN is more predictive of last 4 weeks’ hurries sacks hits rate than first 4 weeks’ HSH rate

(INSERT FIGURE)

@@
